\cvsection{Work Experience}
\begin{cventries}
  \cventry
    {Software Development Engineer Intern}
    {Microsoft Cooperation \quad Windows and Devices Group}
    {Oct. 2015 - Oct. 2016}
    {Shanghai}
    {
      \begin{cvitems}
        \item {Implemented a recommendation system for Microsoft product videos, crawled data from Channel9, YouTube etc., built iOS and Android apps to view and rate videos and created backend service for personalized recommendations with collaborative filtering and content-based filtering algorithms.}
        \item {\color{red} \emph {https://github.com/luckyyd/hackathon-mstube}}
        \item {Built and operated test lab with OpenStack private cloud to maintain daily automatic testing and VMs control.}
        \item {\color{red} \emph {https://github.com/luckyyd/OpenStack-ToolsTeam}}
        \item {Developed a new Bitcoin cryptocurrency framework involving central banks and decentralized blockchain-based transaction ledger.}
        \item {\color{red} \emph {https://github.com/foamliu/FiatCoinNet}}
      \end{cvitems}
    }
  \cventry
    {ARM Software Intern}
    {ARM \quad Software and Service Group}
    {May. 2015 - Aug. 2015}
    {Shanghai}
    {
      \begin{cvitems}
        \item {Deployed ARM mbed IoT sensinode for monitoring office temperature with Lpc1768 mcu. Integrated lighting and humidity data into monitor server with CoAP protocol.}
        \item {Second prize of “ARM Global Innovation Challenge” with Wearable device in African proposal.}
      \end{cvitems}
    }
  \cventry
    {Software Engineer, Apprentice}
    {Dow Chemical Company \quad Information System Department}
    {Apr. 2014 - Aug. 2014}
    {Shanghai}
    {
      \begin{cvitems}
        \item {Re-platformed problem resolution tool to SharePoint: create tool using C\# to migrate data from SQL to SharePoint site. Created hidden column to solve underscore issue for searching.}
        \item {Built a script to search all the users in Yammer environment with RESTful API, and found out dimission employees. Wrote a user guide for clients to set up the script.}
      \end{cvitems} 
    }
\end{cventries}
